Exploring Real Data: A look at AirBnB

### 2017-06-07 ArticleDraft.Rmd
A few heading problems fixed
Fixed tree plots, elbow plot, and minor tweak to intro.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2) # graphics
library(dplyr) # data wrangling
library(cowplot) #plot grids
library(knitr) # fancy tables
library(GGally) # scatterplot matrices
library(tree) # regression trees
library(rpart) #classification trees
library(rpart.plot) #plots of classification trees
library(car) # marginal model plots

@@

According to 
Jonathan Rosenberg, adviser to Larry Page and former SVP of products at Google, 
"Data is the sword of the 21st century, those who weild it well, the samurai."
The world of data and data analysis is growing in importance, and those with the interest and appropriate skillset are uniquely positioned to solve interesting problems and answer vital questions.

@@

###Exploration #6:

@@

#Produces a regression tree:
t<-tree(price~ accommodates+beds+bathrooms +guests_included+review_scores_rating+BT+UD, data = seattle1 )
t
plot(t)
text(t)

#It appears that the most important variable in the data is 'accomodates'.  
#If you just want to split the data into two groups, you should look to
# see if the rental accomodates 5 or more people.  
#     If so, the average price would be $223, 
#     If not the average price would be $102.

#For the rentals which accomodate less than 5 people, 
# the next break occurs depending on 
#    if he rental accomodates three or four people (average price $128.10) 
#    or not (average price $85.51).

#The next break occurs in the rentals that accommodate 5 or more people: 
#     rentals with two or fewer bathrooms (average price $188) 
#     or more than two (average price $326).

@@

#Let's try using only lat/long, and trying to decide what the optimal number of clusters is: 
wcc<-NULL
for(i in 2:10){
  wcc<-c(wcc,sum(kmeans(clusters[,7:8],i)$withinss))	
}
plot(seq(2,10),wcc,type="b",pch=1,xlab="# of Clusters",
     ylab="Within Sum--Squares")
#In the 'elbow plot' above, we look for places where the slope changes drastically

#Suppose you choose 4 clusters: 
km<-kmeans(clusters[,7:8],4)
clusters<-clusters %>% mutate(Predict = km$cluster)
ggplot(clusters, aes(x = longitude, y = latitude, color = as.factor(Predict))) + 
  geom_point()

@@

##Conclusions

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2) # graphics
library(dplyr) # data wrangling
library(cowplot) #plot grids
library(knitr) # fancy tables
library(GGally) # scatterplot matrices
library(rpart) #regression and classification trees
library(rpart.plot) #plots of classification trees
library(car) # marginal model plots

@@

According to 
Jonathan Rosenberg, <!--adviser to Larry Page and--> former SVP of products at Google, 
"Data is the sword of the 21st century, those who weild it well, the samurai."
The world of data and data analysis is growing in importance, and those with the interest and appropriate skillset are uniquely positioned to solve interesting problems and answer vital questions.

@@

### Exploration #6:

@@

#Produces a regression tree:
t<-rpart(price~ accommodates+beds+bathrooms +guests_included+review_scores_rating+BT+UD, data = seattle1 )
t
rpart.plot(t)

#It appears that the most important variable in the data is 'accomodates'.  
#If you just want to split the data into two groups, you should look to
# see if the rental accomodates 5 or more people.  
#     If so, the average price would be $227, 
#     If not the average price would be $104.

#For the rentals which accomodate less than 5 people, 
# the next break occurs depending on 
#    if the rental accomodates four people (average price $140) 
#    or not (average price $91).

#The next break occurs in the rentals that accommodate 5 or more people: 
#     rentals with two or fewer bathrooms (average price $192) 
#     or more than two (average price $324).

@@

#Let's try using only lat/long, and trying to decide what the optimal number of clusters is: 
wss<-NULL
for(i in 2:10){
  wss<-c(wss,sum(kmeans(clusters[,7:8],i)$withinss))
               }
df<-data.frame(x = 2:10, y = wss)
ggplot(df, aes(x = x, y = y)) + geom_line() + geom_point(shape = 7)+
  xlab('# of Clusters') + ylab('Within Sum of Squares') + ggtitle('Elbow Plot')
#In the 'elbow plot' above, we look for places where the slope changes drastically (elbows!)

#Suppose you choose 4 clusters: 
km<-kmeans(clusters[,7:8],5)
clusters<-clusters %>% mutate(Predict = km$cluster)
ggplot(clusters, aes(x = longitude, y = latitude, color = as.factor(Predict))) + 
  geom_point()

@@

## Conclusions
